\begin{document}
\begin{enumerate}
    \item \textbf{Personal computer (PC):} A computer designed for use by an individual, usually incorporating a graphics display, a keyboard, and a mouse.
    
    \item \textbf{Server:} A computer used for running larger programs for multiple users, often simultaneously, and typically accessed only via a network.
    
    \item \textbf{Supercomputer:} A class of computers with the highest performance and cost; they are configured as servers and typically cost tens to hundreds of millions of dollars.
    
    \item \textbf{Terabyte (TB):} Originally 1,099,511,627,776 (2\textsuperscript{40}) bytes, although communications and secondary storage systems developers started using the term to mean 1,000,000,000,000 (10\textsuperscript{12}) bytes. To reduce confusion, we now use the term tebibyte (TiB) for 2\textsuperscript{40} bytes, defining terabyte (TB) to mean 10\textsuperscript{12} bytes. 
    
    \item \textbf{Embedded computer:} A computer inside another device used for running one predetermined application or collection of software.
    
    \item \textbf{Personal mobile devices (PMDs):} Small wireless devices to connect to the Internet; they rely on batteries for power, and software is installed by downloading apps. Conventional examples are smartphones and tablets.
    
    \item \textbf{Cloud Computing:} Large collections of servers that provide services over the Internet; some providers rent dynamically varying numbers of servers as a utility.
    
    \item \textbf{Software as a Service (SaaS):} Delivers software and data as a service over the Internet, usually via a thin program such as a browser that runs on local client devices, instead of binary code that must be installed, and runs wholly on that device. Examples include web search and social networking.
    
    \item \textbf{Systems software:} Software that provides services that are commonly useful, including operating systems, compilers, loaders, and assemblers.
    
    \item \textbf{Operating system:} Supervising program that manages the resources of a computer for the benefit of the programs that run on that computer.
    
    \item \textbf{Compiler:} A program that translates high-level language statements into assembly language statements.
    
    \item \textbf{Binary digit:} Also called a bit. One of the two numbers in base 2 (0 or 1) that are the components of information.
    
    \item \textbf{Instruction:} A command that computer hardware understands and obeys.
    
    \item \textbf{Assembler:} A program that translates a symbolic version of instructions into the binary version.
    
    \item \textbf{Assembly language:} A symbolic representation of machine instructions.
    
    \item \textbf{Machine language:} A binary representation of machine instructions.
    
    \item \textbf{Input device:} A mechanism through which the computer is fed information, such as a keyboard.
    
    \item \textbf{Output device:} A mechanism that conveys the result of a computation to a user, such as a display, or to another computer.
    
    \item \textbf{Liquid crystal display (LCD):} A display technology using a thin layer of liquid polymers that can be used to transmit or block light according to whether a charge is applied.
    
    \item \textbf{Active matrix display:} A liquid crystal display using a transistor to control the transmission of light at each individual pixel.
    
    \item \textbf{Pixel:} The smallest individual picture element. Screens are composed of hundreds of thousands to millions of pixels, organized in a matrix.
    
    \item \textbf{Integrated circuit:} Also called a chip. A device combining dozens to millions of transistors.
    
    \item \textbf{Central processing unit (CPU):} Also called processor. The active part of the computer, which contains the datapath and control and which adds numbers, tests numbers, signals I/O devices to activate, and so on.
    
    \item \textbf{Datapath:} The component of the processor that performs arithmetic operations.
    
    \item \textbf{Control:} The component of the processor that commands the datapath, memory, and I/O devices according to the instructions of the program.
    
    \item \textbf{Memory:} The storage area in which programs are kept when they are running and that contains the data needed by the running programs.
    
    \item \textbf{Dynamic random access memory (DRAM):} Memory built as an integrated circuit; it provides random access to any location. Access times are 50 nanoseconds and cost per gigabyte in 2012 was \$5 to \$10.
    
    \item \textbf{Cache memory:} A small, fast memory that acts as a buffer for a slower, larger memory.
    
    \item \textbf{Static random access memory (SRAM):} Memory built as an integrated circuit, but faster and less dense than DRAM.
    
    \item \textbf{Instruction set architecture:} Also called architecture. An abstract interface between the hardware and the lowest-level software that encompasses all the information necessary to write a machine language program that will run correctly, including instructions, registers, memory access, I/O, and so on.
    
    \item \textbf{Application binary interface (ABI):} The user portion of the instruction set plus the operating system interfaces used by application programmers. It defines a standard for binary portability across computers.
    
    \item \textbf{Implementation:} Hardware that obeys the architecture abstraction.
    
    \item \textbf{Volatile memory:} Storage, such as DRAM, that retains data only if it is receiving power.
    
    \item \textbf{Nonvolatile memory:} A form of memory that retains data even in the absence of a power source and that is used to store programs between runs. A DVD disk is nonvolatile.
    
    \item \textbf{Main memory:} Also called primary memory. Memory used to hold programs while they are running; typically consists of DRAM in today's computers.
    
    \item \textbf{Secondary memory:} Nonvolatile memory used to store programs and data between runs; typically consists of flash memory in PMDs and magnetic disks in servers.
    
    \item \textbf{Magnetic disk:} Also called hard disk. A form of nonvolatile secondary memory composed of rotating platters coated with a magnetic recording material. Because they are rotating mechanical devices, access times are about 5 to 20 milliseconds and cost per gigabyte in 2012 was \$0.05 to \$0.10.
    
    \item \textbf{Flash memory:} A nonvolatile semiconductor memory. It is cheaper and slower than DRAM but more expensive per bit and faster than magnetic disks. Access times are about 5 to 50 microseconds and cost per gigabyte in 2012 was \$0.75 to \$1.00.
    
    \item \textbf{Local area network (LAN):} A network designed to carry data within a geographically confined area, typically within a single building.
    
    \item \textbf{Wide area network (WAN):} A network extended over hundreds of kilometers that can span a continent.
    
    \item \textbf{Transistor:} An on/off switch controlled by an electric signal.
    
    \item \textbf{Very large-scale integrated (VLSI) circuit:} A device containing hundreds of thousands to millions of transistors.
    
    \item \textbf{Silicon:} A natural element that is a semiconductor.
    
    \item \textbf{Semiconductor:} A substance that does not conduct electricity well.
    
    \item \textbf{Silicon crystal ingot:} A rod composed of a silicon crystal that is between 8 and 12 inches in diameter and about 12 to 24 inches long.
    
    \item \textbf{Wafer:} A slice from a silicon ingot no more than 0.1 inches thick, used to create chips.
    
    \item \textbf{Die:} The individual rectangular sections that are cut from a wafer, more informally known as chips.
    
    \item \textbf{Yield:} The percentage of good dies from the total number of dies on the wafer.
    
    \item \textbf{Response time:} Also called execution time. The total time required for the computer to complete a task, including disk accesses, memory accesses, I/O activities, operating system overhead, CPU execution time, and so on.
    
    \item \textbf{Throughput:} Also called bandwidth. Another measure of performance, it is the number of tasks completed per unit time.
    
    \item \textbf{CPU execution time:} Also called CPU time. The actual time the CPU spends computing for a specific task.
    
    \item \textbf{User CPU time:} The CPU time spent in a program itself.
    
    \item \textbf{System CPU time:} The CPU time spent in the operating system performing tasks on behalf of the program.
    
    \item \textbf{Clock cycle:} Also called tick, clock tick, clock period, clock, or cycle. The time for one clock period, usually of the processor clock, which runs at a constant rate.
    
    \item \textbf{Clock period:} The length of each clock cycle.
    
    \item \textbf{Clock cycles per instruction (CPI):} Average number of clock cycles per instruction for a program or program fragment.
    
    \item \textbf{Instruction count:} The number of instructions executed by the program.
    
    \item \textbf{Instruction mix:} A measure of the dynamic frequency of instructions across one or many programs.
    
    \item \textbf{Workload:} A set of programs run on a computer that is either the actual collection of applications run by a user or constructed from real programs to approximate such a mix. A typical workload specifies both the programs and the relative frequencies.
    
    \item \textbf{Benchmark:} A program selected for use in comparing computer performance.
    
    \item \textbf{Million instructions per second (MIPS):} A measurement of program execution speed based on the number of millions of instructions. MIPS is computed as the instruction count divided by the product of the execution time and $10^6$.
\end{enumerate}
\end{document}

